\Large The psychological arrow of time drives temporal asymmetries in inferring unobserved past and future events

### 2023-09-21 paper/main.tex
added references recommended by reviewer 4

People's knowledge asymmetries are not always directly observable. For example,
in a conversation where someone talks exclusively about their future plans, a
passive observer might gain more insight into the speaker's unobserved future
than their unobserved past. However, because the speaker is also guided by
their own psychological arrow of time, the ``upper limit'' of knowledge about
their past is still higher than that of their future. Therefore, after
accounting for knowledge that \textit{could} be revealed through active
participation in the conversation, the seemingly future-biased conversation
masks an underlying knowledge asymmetry in favor of the past. This hypothesized
``unmasking'' effect of interaction implies that the influence of other
people's psychological arrows of time should be more robust when the receiver
is an active participant in the conversation. Other social dimensions, such as
trust, motivation or level of engagement, personal goals, and beliefs, might
serve to modulate the effective ``gain'' of the communication channel-- i.e.,
how much the speaker's knowledge influences the observer's knowledge.

>>>>

People's knowledge asymmetries are not always directly observable. For example,
in a conversation where someone talks exclusively about their future plans, a
passive observer might gain more insight into the speaker's unobserved future
than their unobserved past. However, because the speaker is also guided by
their own psychological arrow of time, the ``upper limit'' of knowledge about
their past is still higher than that of their future. Therefore, after
accounting for knowledge that \textit{could} be revealed through active
participation in the conversation, the seemingly future-biased conversation
masks an underlying knowledge asymmetry in favor of the past. This hypothesized
``unmasking'' effect of interaction implies that the influence of other
people's psychological arrows of time should be more robust when the receiver
is an active participant in the conversation. Other social dimensions, such as
trust, motivation or level of engagement, personal goals, and beliefs, might
serve to modulate the effective ``gain'' of the communication channel-- i.e.,
how much the speaker's knowledge influences the observer's knowledge. Some
recent work~\citep[e.g.,][]{TamiMitc13, MeyeEtal19b} also suggests that people
might use ``mental simulations'' of how other people might respond in
particular situations (e.g., in the future), or of which sorts of prior
experiences might have led someone to behave a particular way in the present.
